Wu-Tang Clan

### 2015-03-19 rmtw/a6/latex8.tex
Added authorblock

\documentclass[10pt,twocolumn]{article} 
\usepackage{latex8}
%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{A Comparison of Use-Case Based and Checklist-
Based Reading: A Controlled Experiment}

% author names and affiliations
\author{John Burchell and William Granli \\
john.a.burchell, william.granli@gmail.com}

\maketitle
\thispagestyle{empty}

%-------------------------------------------------------------------------

@@

The sections following the Introduction are structured as follows: In Section II, we present a literature review on research related to our study. Section II describes the case company and how it was selected. A description of our methodology is introduced in Section III.

@@

\section{Related Work}
Our work is mainly related to the research area of APIs. This discipline will be discussed in both section 2.1 and 2.2. Our research is directly related to the fields of software evolution and software ecosystems. Section 2.2 will describe APIs in the context of those two fields.

>>>>

\documentclass[10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{authblk}

\title{Wu-Tang Clan}

% \author[*]{John Burchell}
% \author[x]{William Granli}
% \affil[*x]{Software Engineering \& Management}
% \affil[*x]{University Of Gothenburg}
% \affil[*]{john.a.burchell@gmail.com}
% \affil[x]{william.granli@gmail.com}

\begin{document}

\author{\textsuperscript{*}John Burchell \qquad \textsuperscript{x}William Granli \\
		\textsuperscript{*}john.a.burchell@gmail.com \qquad \textsuperscript{x}william.granli@gmail.com \\
		\textsuperscript{*x}Software Engineering \& Management  \\
		\textsuperscript{*x}University of Gothenburg }

\maketitle

@@

%Structure of the paper
The sections following the Introduction are structured as follows: In Section II, we present a literature review on research related to our study. Section II describes the case company and how it was selected. A description of our methodology is introduced in Section III.

@@

\section{Related Work}
Our work is mainly related to the research area of API design. This discipline is discussed in Section 2.1. The motives and effects of changes to APIs is directly related related to the fields of software evolution and software ecosystems, and this will be discussed in Section 2.2.
